---
title: "Hemispherical Photo Light Analysis"
author: "Kateri Salk"
date: "12/30/2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---


## Setup 

Code and help files for Hemiphot found at https://github.com/naturalis/Hemiphot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("Hemiphot.R") 
library(jpeg)
library(tidyverse)

theme_set(theme_classic())

siteyear <- read.csv("../R_DataProcessing/CSVs/SiteYear.csv")
```

## testing
This is just to see if the test.hemi function is cropping the circle correctly. Can swap in any photo file into the "test" line.

Note: the function identifies the black part of the circle as part of the circle if the photo has black space above and below. Crop photos to square format so that the function identifies only the photo.
```{r}
test <- readJPEG("../../../Source/Received/NDS Hemispherical Photos/Cropped/20140806,_Vallecito Creek, 9372, hemispherical, NDS Harvest 2014, Sampling,HDR.jpg")

test.hemi <- Image2Hemiphot(test)

PlotHemiImage(test.hemi)

```

## Batch Processing
### Color photos

```{r}
days = seq(15,360,30)   # roughly each mid of the 12 months

### Location parameters
location.latitude   = 38 # middle latitude of CO sites. CanOpen and LAI do not use this.
location.day        = 222 # middle longitude of CO sites. CanOpen and LAI do not use this.
location.days       = seq(15,360,30)   # roughly each mid of the 12 months

### Image parameters
## determine in Hemiphot.R and fill in here for batch processing
location.cx         = 1504             # x coordinate of center
location.cy         =  975             # y coordinate of center
location.cr         =  900             # radius of circle
location.threshold  = 0.65

### atmospheric parameters
location.tau        = 0.6
location.uoc        = 0.15
### We assume colour images
### in a subdirectory images
### load all JPG file names in a list

all.images = list.files("../../../Source/Received/NDS Hemispherical Photos/Cropped/",
                        pattern = ".jpg")
nr.images = length(all.images); nr.images

## Create data frame to hold all results
all.data = data.frame(matrix(0, nr.images, 7))
names(all.data) = c("File", "CanOpen", "LAI",
                    "DirectAbove", "DiffAbove",
                    "DirectBelow", "DiffBelow")
all.data[,1] = all.images

## now the batch can start
t1 = Sys.time()
for(i in 1:nr.images){    
  ## read file
  image = readJPEG(paste("../../../Source/Received/NDS Hemispherical Photos/Cropped/",
                         all.images[i],sep = ""), native = F)     
  #if native = T creates a raster, else an array

  ## conver to Hemi image
  image = Image2Hemiphot(image)

  ## set cirlce parameters
  image = SetCircle(image, cx = location.cx, cy = location.cy, cr = location.cr)

  ## select blue channel
  image = SelectRGB(image, "B")

  #threshold
  image = ThresholdImage(im = image, th = location.threshold, draw.image = F)

  # canopy openness
  gap.fractions = CalcGapFractions(image)
  all.data[i,2] = CalcOpenness(fractions = gap.fractions)
   
  ## calculate LAI according to Licor's LAI Analyzer 
  all.data[i,3] = CalcLAI(fractions = gap.fractions)

  ## Photosynthetic Photon Flux Density (PPDF, umol m-1 s-1) P
  rad = CalcPAR.Day(im = image,
                    lat = location.latitude, d = days,
                    tau = location.tau, uoc = location.uoc, 
                    draw.tracks = F, full.day = F)
  all.data[i,4] = rad[1]
  all.data[i,5] = rad[2]
  all.data[i,6] = rad[3]
  all.data[i,7] = rad[4]
}
t2 = Sys.time()

##time per image
(t2 - t1)/nr.images

# process dataset
hemiphoto.df <- all.data %>%
  select(File, CanOpen, LAI)%>%
  separate(File, into = c("Date", "File"), ",_") %>%
  separate(File, into = c("Site", "File"), ", hemispherical, NDS ") %>%
  separate(File, into = c("Junk" , "Replicate"), "2014, ") %>%
  separate(Replicate, into = c("Replicate", "Junk2"), ".jpg") %>%
  separate(Site, into = c("Site", "SiteCode"), ", ") %>%
  select(-Junk, -Junk2)

hemiphoto.df$Date <- as.Date(hemiphoto.df$Date, "%Y%m%d")

## save data
write.csv(hemiphoto.df, "./Output/HemiPhotoOutput.csv", row.names = FALSE)
```

### Black and white photos

```{r}
days = seq(15,360,30)   # roughly each mid of the 12 months

### Location parameters
location.latitude   = 38 # middle latitude of CO sites. CanOpen and LAI do not use this.
location.day        = 222 # middle longitude of CO sites. CanOpen and LAI do not use this.
location.days       = seq(15,360,30)   # roughly each mid of the 12 months

### Image parameters
## determine in Hemiphot.R and fill in here for batch processing
location.cx         = 1504             # x coordinate of center
location.cy         =  975             # y coordinate of center
location.cr         =  900             # radius of circle
location.threshold  = 0.65

### atmospheric parameters
location.tau        = 0.6
location.uoc        = 0.15
### We assume colour images
### in a subdirectory images
### load all JPG file names in a list

all.images.bw = list.files("../../../Source/Received/NDS Hemispherical Photos/BW/Cropped/",
                           pattern = ".jpg")
nr.images.bw = length(all.images.bw); nr.images.bw

## Create data frame to hold all results
all.data.bw = data.frame(matrix(0, nr.images.bw, 7))
names(all.data.bw) = c("File", "CanOpen", "LAI",
                    "DirectAbove", "DiffAbove",
                    "DirectBelow", "DiffBelow")
all.data.bw[,1] = all.images.bw

## now the batch can start
t1 = Sys.time()
for(i in 1:nr.images.bw){    
  ## read file
  image = readJPEG(paste("../../../Source/Received/NDS Hemispherical Photos/BW/Cropped/",
                         all.images.bw[i],sep = ""), native = F)     
  #if native = T creates a raster, else an array

  ## conver to Hemi image
  image = Image2Hemiphot(image)

  ## set cirlce parameters
  image = SetCircle(image, cx = location.cx, cy = location.cy, cr = location.cr)

  ## select blue channel
  image = SelectRGB(image, "B")

  #threshold
  image = ThresholdImage(im = image, th = location.threshold, draw.image = F)

  # canopy openness
  gap.fractions = CalcGapFractions(image)
  all.data.bw[i,2] = CalcOpenness(fractions = gap.fractions)
   
  ## calculate LAI according to Licor's LAI Analyzer 
  all.data.bw[i,3] = CalcLAI(fractions = gap.fractions)

  ## Photosynthetic Photon Flux Density (PPDF, umol m-1 s-1) P
  rad = CalcPAR.Day(im = image,
                    lat = location.latitude, d = days,
                    tau = location.tau, uoc = location.uoc, 
                    draw.tracks = F, full.day = F)
  all.data.bw[i,4] = rad[1]
  all.data.bw[i,5] = rad[2]
  all.data.bw[i,6] = rad[3]
  all.data.bw[i,7] = rad[4]
}
t2 = Sys.time()

##time per image
(t2 - t1)/nr.images.bw

# R didn't like the name of this site, so the name of the file was set to "test.jpg" and fixed here.
all.data.bw$File[all.data.bw$File == "test.jpg"] <- "20140812_Cochetopa Creek @ Sillsville, 10322, hemispherical, NDS Harvest 2014, Sampling-Clipped.jpg"
hemiphoto.df.bw <- all.data.bw %>%
  select(File, CanOpen, LAI) %>%
  separate(File, into = c("Date", "File"), "_") %>%
  separate(File, into = c("Site", "File"), ", hemispherical, NDS") %>%
  separate(Site, into = c("Site", "SiteCode"), ", ") %>%
  select(-File)

hemiphoto.df.bw$Date <- as.Date(hemiphoto.df.bw$Date, "%Y%m%d")

## save data
write.csv(hemiphoto.df.bw, "./Output/HemiPhotoOutput_BW.csv", row.names = FALSE)
```